\documentclass{article}

\title{XMRGO: A Privacy Focused Platform For Contractual Money} 

\author{
    Alyosha Fedorov\\
    alyosha.fedorov@protonmail.com\\
    Rev. 0
}

\date{}
%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%

\begin{document} 

\maketitle 

\begin{abstract}
    XMRGO is the combination of Ergo and Monero. A privacy-oriented currency 
    and smart contract platform. Taking the best of both worlds to create a 
    new form of private smart money. The combination comes from the smart 
    contract capabilities of Ergo and the privacy of Monero. Monero is a 
    private and fungible currency. Ergo is the next generation smart 
    contract platform. The goal of XMRGO is to create a completely 
    anonymous, unlinkable, and untraceable smart contract platform.
\end{abstract}

\section*{Why Ergo and Monero?}

\indent Ergo is the top-of-the-line smart contract platform for PoW. Monero 
is the top-of-the-line privacy coin for PoW. Combing their powers together 
will create the most private and technologically advance smart contract and 
currency blockchain. This is no easy feat but it must be done to ensure that 
the future of blockchain technology will not be ruined.

\subsection*{Privacy-based Finance}

\indent This coin is not meant to be sold on centralized exchanges, CEX, where 
the know-your-customer, KYC, is dominant and well-practiced. The XER coin 
should only be obtainable via decentralized exchanges, peer-to-peer trading, 
and mining rewards. It is a coin for those to have the option out of the 
standard practices of cryptocurrencies, ruining privacy for maximizing 
profits, e.g. informing CEX to require view keys like in Monero. This is a 
coin for true privacy while allowing smart contracts to exist for complex 
financial transactions. The project will always remain open-source. It is built 
by developers working towards the dream of financial freedom and untraceable 
smart money.


\subsection*{XMRGO Protocol}

\indent The Xmrgo protocol is a combination of Ergo and Monero. It blends the 
vision of Ergo and Monero into a single entity for a singular purpose. It is 
designed to be a privacy-based decentralized finance platform.

\subsection*{Key Features}
\begin{itemize}
    \item Smart Contracts Using $\Sigma$-protocols
    \item Modified Ergo + Monero Emission Rate
    \item RandomX Consensus Protocol
    \item Monero transaction security
\end{itemize}

\section*{The XMRGO Vision}

\indent Xmrgo is very private and can only be changed in the future by the 
community. There exist many principles that should be followed in Xmrgo. 
In case of intentional violation of any of these principles, the resulting 
protocol should not be called XMRGO.

\subsection*{Decentralization First}

\indent Xmrgo should be as decentralized as possible: any parties whose 
absence or malicious behavior may affect the security of the network should 
be avoided at all cost.

\subsection*{Created for Private People}

\indent Xmrgo is a platform for private people, and their interests should 
not be infringed upon in favor of big parties.

\subsection*{A Platform for Contractual Private Money}

\indent Xmrgo is the base layer to applications that will be built on top of 
it. Its main focus is to provide an efficient, secure, and easy way to 
implement private financial contracts.

\subsection*{Long-term Focus}

\indent All aspects of Xmrgo development should be focused on a long-term 
perspective.

\subsection*{Permissionless and Open}

\indent Xmrgo protocol does not restrict or limit any categories of usage.

\subsection*{RandomX Consensus}

\indent Xmrgo utilizes the Proof of Work (PoW) consensus protocol called RandomX.

\subsection*{Untraceability and Unlinkability of Transactions}

\indent All possible senders are equiprobable and it should be impossible to 
prove that any transaction was sent to the same person.

\section*{Implementation}

\indent At the core, XMRGO is just Ergo with a different PoW consensus 
protocol, emission schedule, and default privacy features. It utilizes the 
$\Sigma$-protocols to create Monero-style transactions for complete 
anonymity, untraceability, and unlinkability. The resulting blockchain should 
have the smart contract capabilities of Ergo with the privacy of Monero.

\indent This is great news for building this new blockchain. The required 
pieces already exist. All that must be done is putting the pieces together 
in the correct combination such that the dream of a completely private and 
untraceable smart contract platform will come to fruition.

\subsection*{Parameters}

\begin{table}[h!]
\begin{center}
    \begin{tabular}{l|r} % <-- Alignments: 1st column left, 2nd middle and 3rd right, with vertical lines in between
    \hline
    Block Reward & 1 XER + Fees per Block\\
    Max Supply & $\infty$\\
    Fee & 0.001 XER per kB\\
    Block Time & 2 Minutes per Block\\
    Consensus Algorithm & RandomX\\
    Language & ErgoScript\\
    Block Size & Arbitrary\\
    eUTXO Tax & 4 years\\
    \end{tabular}
\end{center}
\end{table}

\indent Unlike Ergo, there will not be a treasury for dApp development. All fees will go directly to the miners from the first block until infinity.

\clearpage

\noindent XMRGO believes privacy-based decentralized finance is the future of money.

\end{document}
